### 2020-10-14 Thesis-Chapter1-Introduction.tex
Update notes on five-eyes communiques

The conversation over encryption is in a stalemate. Governments and law enforcement agencies frequently cite the need to
access encrypted data to perform their duties \cite{ministerial_2018} \cite{fbi_2020}. Human rights groups and technical
leaders counter that a weakened encryption environment would fatally compromise privacy and security as we know it
\cite{ruiz_there_2018} \cite{abelson_2015}. As the debate continues, sides have become entrenched, and both sides have
engaged in disingenuous attacks against their opponents.

>>>>

The conversation over encryption is in a stalemate. Governments and law enforcement agencies frequently cite the need to
access encrypted data to perform their duties \cite{ministerial_2018} \cite{intl_2020} \cite{fbi_2020}. Human rights
groups and technical leaders counter that a weakened encryption environment would fatally compromise privacy and
security as we know it \cite{abelson_2015} \cite{eightythree_2017} \cite{ruiz_there_2018}. As the debate continues,
sides have become entrenched, and both sides have engaged in disingenuous attacks against their opponents.
